Automated topic naming to support analysis of software maintenance activities

### 2011-01-14 msr/msr2011.tex
prototype with neil's intro. It seems much simpler to me. Maybe expand a little on the benefits.

\todo[inline]{neil: possible reword: Topic modeling is a machine learning technique which creates multinomial distributions over words found in a text corpus. Topic models are useful in software engineering because they can identify, from text corpora such as source code, change logs, email, and others, co-occuring words. For example, a topic extracted from a set of changelogs might be ``listener change remove add fire''. A topic model gives developers an overview of where activity is occurring and gives managers or maintainers a sense of project history. A major challenge is to accurately identify the label for a topic (in the previous case, perhaps ``event-handling''). Current approaches are manual: they rely on human expertise to recognize the appropriate label. Furthermore, to date the results of topic modeling are project specific, and not generalizable. }

% An attempt Motivate topics
%XXX is this the correct terminology for commits/revisions
%The development of software does not occur in a vacuum, 
Revisions to
source code are not independent of past revisions, the specification or
the task at hand.
Often the purpose of revisions to source code relate to one or more topics, whether it be a maintenance activity, a quality issue, a requirement or feature or a response to a bug report.
Many of these purposes and tasks exhibit themselves as latent topics which cross-cut and compose many of development artifacts: version control revisions, bug reports, and mailing-list discussions.
\todo[inline]{NeiL: I still find this clumsily worded}

Topics in software engineering practice refer to specific shared threads of discussions between project stakeholders. 
These topics can include particular requirements, maintenance requests, bug fixes or other software engineering tasks. %NEIL: define topic specifically as akin to email 'thread'. It sounded too vague. Also changed from 'developers' to 'stakeholders' because developers sounds too coding oriented. Our work could apply to testers, users, etc.
While addressing a topic of development, stakeholders often produce or modify multiple development artifacts.
%
These artifacts can include source code, bug reports, revisions to source code, and test cases. 
%
Topics are typically latent, i.e., not explicitly named, and can be in several potential states: they may not be immediately resolved, they may re-occur, yet others are only dealt with briefly  (e.g., a bug report that is closed)
Within this paper we define \emph{topics} as latent word distributions that describe and compose the documents (version control commits) being analyzed. 
We define \emph{labelled topics} as \emph{topics} that have been interpreted and labelled. 
The distinction is important because word distributions can consistent of many words, thus if one has many topics, reading and interpreting these words is prohibitive.
For example, if you read only 10 words per topic from 500 topics you have to read and interpret 5000 words, this is 5 or more pages of text!
Thus \emph{labelled topics} save interpretation time.

There are many practical applications of \emph{labelled topic
  extraction} 
ranging from summarization, project dashboards, and software process recovery.
These methods are useful for providing abstractions of development activities and artifacts.
Particularly in large projects, summarization of developer activities is essential to maintenance. 
Rather than looking for specific concepts in a project~\cite{marcus04wcre}, we are interested in understanding a software project relative to common properties of all software.
We can improve project dashboards, used by managers, by showing both the current topics of development as well those that relate to domain-independent taxonomies, such as NFRs.
Some quality assurance questions can be addressed by seeking evidence within repositories that NFR-related topics are being addressed.
Topic modelling can be used to check if development is on track and focused.
For outside users of the software, our technique can provide insight into that company's development practices in order to answer questions such as, ``Are they focused on usability?''
Within the organization \emph{labelled topic extraction} can act as a historical sanity check, used to avoid \emph{confirmation bias}, which is the difference between what people think happened and what actually happened. 
Some software releases, for instance, are poorly received since they are quite buggy. 
Our technique would help explain why this was the case, since it can identify NFRs which are dominating developer attention.
Thus developers can use these techniques to get an overview of the current and past development topics.
For awareness, managers can use these techniques to gain an overview of topics of development.

% This is a very long example it'd be nice if it was tighter
% Perhaps development has been sidetracked by cascading issues that appeared during implementation.
% For instance, a developer adding an optimization to a RDBMS might have to change multiple modules in order to provide that optimization code with enough information to operate. 
% This issue might trigger a series of cascading changes that might be difficult to discover when trying to explain why the project's release date has been missed. 
% Labelled Topic extraction could be used to detect this distinct focus of development.

% semi-automatically sounds too uncertain. I think the introduction can be more muscular and bold. Don't give the reviewer any room to start doubting.

% why are topics useful
Developers often interact with abstractions of the artifacts from which topics are derived, rather than the artifacts themselves.
Such abstractions include project dashboards~\cite{kersten2005mylar} and tags~\cite{treude2010}%, and complexity metrics \cite{mccabe1976complexity}. 
Without the structured information which dashboards typically rely on, topics become a valuable and automatically extractable abstraction of software artifacts.
Topics abstract software artifacts by their subject matter, rather than their concrete representation. 
Much like aspect-oriented programming, topic labeling can identify cross-cutting concerns in a software project (as in~\cite{Baldi2008}).
The topics of development are relevant because they identify the distinct issues facing stakeholders at a particular time.

The goal of concept location and topic analysis research is to recover these topics and the related software artifacts.
% get neil's data mining point in there
To date, the results of topic analysis and concept location are project specific, and not generalizable.
% get the interpretation aspect
Much of the current research stops short of automatically interpreting the purpose of the topic, e.g.~\cite{Baldi2008,Kuhn2007,marcus04wcre}. 
That is, extracted topics are usually manually named and labelled by those who read the topic words.

% topics are numerous?
Deriving and labelling topics is a challenging machine learning problem. 
Topic analysis produces % raw topics that are represented as
 unlabelled context-free word-lists or word distributions.
Topics have to be identified by interpreting the prevalent words in a word distribution and by inspecting related documents. 
This manual approach is impractical when handling hundreds of different topics. To scale to large projects (thousands of lines of code and multiple releases), we need automatic assistance to determine the topic label.
We propose a method of interpreting and labelling topics, and their related artifacts, that is generalizable and relevant to multiple projects.

@@

Cleland-Huang and her colleagues published work on mining requirements documents for non-functional requirements (NFR) (quality requirements)~\cite{Cleland-Huang2006}. 
Their approach was similar to ours, as they mined keywords from their own NFR catalogues~\cite{chung99}.
%One approach they tried was similar to this one, with keywords mined from NFR catalogues found in their previous work~\cite{chung99}. 
They managed a recall of 80\% with precision of 57\% for the Security NFR, but could not find a reliable source of keywords for other NFRs. 
Instead, they developed a supervised classifier by using human experts to identify an NFR training set. 
Our worked differed because we had a more comprehensive set of terms based on the taxonomy we chose.
We also wanted a common taxonomy that allows us to make cross-project comparison; this was not one of their objectives.
The objective of Cleland-Huang's study was to identify new NFRs for system development, yet our objective was to recover those latent NFRs from commit-log messages of the project. 
Another difference was that our data was far less structured than the requirements documents used in their study.
%There are several reasons we did not follow this route. 
%One, we believe we have a more comprehensive set of terms due to the taxonomy we chose. 
%Secondly, we wanted to compare across projects. 
%Their technique was not compared across different projects and the applicability of the training set to different corpora is unclear. 
%A common taxonomy allows us to make cross-project comparison. 
%Although subject to the assumption that all projects conceive of these terms in the same way.
%Thirdly, while the objective of Cleland-Huang's study was to identify new NFRs (for system development) our study assumes these NFRs are latent in the commit-log messages of the project.

@@

To evaluate our approach, we sought candidate systems that were mature projects and had openly accessible source control repositories. 
We selected systems from the same application domain, so the functional requirements would be broadly similar. 
We selected MySQL 3.23 and MaxDB 7.500 as they were open-source, partially-commercial database systems. 
MaxDB started in the late 1970s as a research project, and was later acquired by SAP. 
As of version 7.500, released April 2007, the project has 940 thousand lines of C source code\footnote{generated using David A. Wheeler's \emph{SLOCCount}.}. 
The MySQL project started in 1994 and MySQL 3.23 was released in early 2001. 
MySQL contains 320 thousand lines of C and C++ source code.  
Choosing an older version of these projects allowed us to focus on projects which have moved further into the maintenance phase of the software life-cycle.

@@

\noindent \textbf{Creating a validation corpus} --- For MySQL 3.23 and MaxDB 7.500, we manually annotated each extracted topic in each period with the same NFR labels as \textsf{exp2} (software qualities). 
We looked at each period's topics, and assessed what the data --- consisting of the frequency-weighted word lists and messages --- suggested was the topic for that period. 
We were able to pinpoint the appropriate label using auxiliary information as well, such as the actual revisions and files that were related to the topic being annotated.
For example, for the MaxDB topic consisting of a message ``exit() only used in non NPTL LINUX Versions'', we tagged that topic \emph{portability}. 
We compared against this data-set, but we also used the data-set for our supervised machine learning based topic classification. 
% A topic may have more than one matching keyword. % ok what?
%\todo[inline]{inter-rater reliability }
% \todo[inline]{There should be a section here which is about manual annotation. It is really important and it is required by both analyses. Plus we can tell them how.}

@@

% word list similarity
Using our three word lists (\textsf{exp1}, \textsf{exp2}, \textsf{exp3}), we labeled our topics where there was a match between a word in the list and the same word in the topic.
A \emph{named topic} is a topic with a matching label. 
There are roughly 20 times the number of topics as there are periods per project. 
This is because LDA extracted 20 topics per period. 
All experiments were run on MaxDB 7.500 and MySQL 3.23 data.
Table \ref{tbl:wordlist} shows how many topics were labelled for MaxDB
and MySQL.

@@

\noindent \textbf{Analysis of the unsupervised labelling} -- Based on the labels, and our manual topic labelling, 
we compared the results of the unsupervised word matching approach. 
For each quality we assessed whether unsupervised labels matched the manual annotations.
Figure \ref{fig:maxdb-unsup-results} shows our results for MaxDB and MySQL. 
Our performance is measured using the Receiver Operating Characteristic area-under-curve value~\cite{Fawcett2006861}, abbreviated \emph{ROC}. 
ROC values provide a score, similar to school letter-grades (A is 0.9, C is 0.6), reflecting how well a particular learner performed for the given data. 
ROC maps to the more familiar concepts of precision/sensitivity and recall/specificity: it plots the true positive rate (sensitivity) versus the false positive rate (1 - specificity). 
A perfect learner has a ROC value of 1.0, reflecting perfect recall and precision. 
A ROC result of 0.5 would be equivalent to a random learner (that is, issuing as many false positives as true positives). 
The area under the ROC of a classifier is equivalent to the probability that the classifier will rank a randomly chosen positive instance higher than a randomly chosen negative instance.

%\todo[inline]{since ROC is new-sounding, I wonder if a more lengthy explanation would be merited. An obvious question is why not precision/recall? -- ROC is hot right now and it combines both}
% Rebuttal: ROC is not new and it is what the machine learning community, search based software engineering and now the MSR community are using +  it has natural meaningful quality mappings.
\begin{figure*}
  \centering
 \includegraphics[width=0.6\textwidth]{figures/unsupervised-bar}
 \caption{Performance, ROC values (range: 0-1), of unsupervised topic labelling for
   each NFR and per word-list. This graph shows how well the
   unsupervised topic labelling matched our manual annotations.}

%\todo[inline]{this is too tiny in print}
  \label{fig:maxdb-unsup-results}
\end{figure*}

% EXP2
For \textsf{exp2}, the average F-measure (macro-F1) for MaxDB was $0.24$ with a range $0.091$ to
$0.37$, and $0.16$ for MySQL with a range of $0$ to $0.41$.
MaxDB had an average precision and recall of $0.25$ and $0.22$
while MySQL had $0.41$ and $0.10$ respectively.

@@

Based on these results we find that \emph{reliability} and \emph{usability} worked well for MaxDB in \textsf{exp2} and better in \textsf{exp3}. 
MySQL had reasonable results within \textsf{exp2} for \emph{reliability} and \emph{efficiency}. 
MySQL's results for \emph{efficiency} did not improve in \textsf{exp3} but other qualities such as \emph{functionality} did improve. 
If a \emph{C} grade performance has a ROC value of $0.6$ then most of these tests scored a grade of \emph{C} or less, but our classifier nonetheless performed substantially better than random.

% \begin{comment}
% maxdb

% portability,0.773778920308,0.228070175439,76,12,0.181684100119,0.52,0.14606741573,0.553033707865,288,0.96,13
% efficiency,0.832904884319,0.21686746988,36,29,0.124642098177,0.236842105263,0.2,0.557848837209,315,0.915697674419,9
% reliability,0.714652956298,0.379888268156,7,104,0.340426350577,0.246376811594,0.829268292683,0.765208858985,244,0.701149425287,34
% functionality,0.902313624679,0.0952380952381,32,6,0.0834236909204,0.25,0.0588235294118,0.520961060481,349,0.983098591549,2
% maintainability,0.796915167095,0.0919540229885,76,3,0.122505166175,0.571428571429,0.05,0.520145631068,306,0.990291262136,4
% usability,0.830334190231,0.175,11,55,0.138109307712,0.112903225806,0.388888888889,0.620320455226,316,0.851752021563,7

% total,0.808483290488,0.235897435897,238,209,0.126930463023,0.248201438849,0.224755700326,0.560823829443,1818,0.896891958559,69mysql

% portability,0.616040955631,0.137931034483,225,0,0.211497874858,1.0,0.0740740740741,0.537037037037,343,1.0,18
% efficiency,0.924914675768,0.3125,33,11,0.297817974114,0.47619047619,0.232558139535,0.606150156324,532,0.979742173112,10
% reliability,0.726962457338,0.411764705882,61,99,0.242477699079,0.361290322581,0.478632478632,0.633772529295,370,0.788912579957,56
% functionality,0.457337883959,0.0245398773006,315,3,0.00597425429824,0.571428571429,0.012539184953,0.500651614948,264,0.988764044944,4
% maintainability,0.686006825939,0,184,0,0,0,0.0,0.5,402,1.0,0
% usability,0.919795221843,0.175438596491,27,20,0.13508225345,0.2,0.15625,0.560074458484,534,0.963898916968,5

% total,0.721843003413,0.159793814433,845,133,0.0857635592199,0.411504424779,0.0991471215352,0.523778370698,2445,0.9484ahindle@wish:~/projects/lda-paper/src/validate$ cat NOTES 
% columns of maxdb.report.text

%     out['accuracy'] = acc
%     out['f1'] = f1
%     out['fn'] = fn
%     out['fp'] = fp
%     out['mcc'] = mcc
%     out['precision'] = pre
%     out['recall'] = rec
%     out['roca'] = roca
%     out['tnr'] = tnr
%     out['tn'] = tn
%     out['tp'] = tp

% cat exp3.*.report.txt 
% maxdb

% portability,0.706940874036,0.472222222222,38,76,0.286382363909,0.40157480315,0.573033707865,0.659850187266,224,0.746666666667,51
% efficiency,0.372750642674,0.222929936306,10,234,0.067549899325,0.130111524164,0.777777777778,0.548772609819,110,0.31976744186,35
% reliability,0.434447300771,0.256756756757,3,217,0.195966959965,0.149019607843,0.926829268293,0.651633024951,131,0.376436781609,38
% functionality,0.53470437018,0.236286919831,6,175,0.186902353269,0.137931034483,0.823529411765,0.665285832643,180,0.507042253521,28
% maintainability,0.627249357326,0.337899543379,43,102,0.111672018872,0.26618705036,0.4625,0.566201456311,207,0.669902912621,37
% usability,0.27763496144,0.107936507937,1,280,0.0937953415493,0.0572390572391,0.944444444444,0.594863731656,91,0.245283018868,17

% total,0.492287917738,0.257983719474,101,1084,0.0926022435775,0.159689922481,0.671009771987,0.568114654124,943,0.46521953626,206
% mysql

% portability,0.616040955631,0.412532637076,164,61,0.170139234681,0.564285714286,0.325102880658,0.57363015753,282,0.822157434402,79
% efficiency,0.532423208191,0.184523809524,12,262,0.124342460899,0.105802047782,0.720930232558,0.619212814253,281,0.517495395948,31
% reliability,0.588737201365,0.404938271605,35,206,0.209194239572,0.284722222222,0.700854700855,0.630811145737,263,0.560767590618,82
% functionality,0.622866894198,0.651968503937,112,109,0.240455709256,0.655063291139,0.648902821317,0.620331560471,158,0.591760299625,207
% maintainability,0.621160409556,0.218309859155,153,69,-0.00390279540262,0.31,0.16847826087,0.498418234912,333,0.828358208955,31
% usability,0.358361774744,0.104761904762,10,366,0.0128981856383,0.0567010309278,0.6875,0.513425090253,188,0.339350180505,22

% total,0.556598407281,0.367032074706,486,1073,0.058598680978,0.296393442623,0.481876332623,0.532831106575,1505,0.583785880528,452
% \end{comment}

>>>>

Topic modeling is a machine learning technique which creates multinomial distributions over words found in a text corpus. Topic models are useful in software engineering because they can identify, from text corpora such as source code, change logs, email, and others, co-occuring words. For example, a topic extracted from a set of changelogs might be ``listener change remove add fire''. A topic model gives developers an overview of where activity is occurring and gives managers or maintainers a sense of project history. A major challenge is to accurately identify the label for a topic (in the previous case, perhaps ``event-handling''). Current approaches are manual: they rely on human expertise to recognize the appropriate label. Furthermore, to date the results of topic modeling are project specific, and not generalizable.

Changes to software systems, revisions, do not occur without
reason. 
The reason or purpose is often related to requirements 
Often one revision might have multiple purposes ranging from
maintenance issues, quality issues, requirements, features or a
response to a bug report.
These purposes often are exhibited as latent topics that relate to
many development artifacts such as:
 version control revisions, bug reports, and mailing-list discussions.

@@

Cleland-Huang and her colleagues published work on mining requirements documents for non-functional requirements (NFR) (quality requirements)~\cite{Cleland-Huang2006}. 
Their approach was similar to ours, as they mined keywords from their own NFR catalogues~\cite{chung99}.
%One approach they tried was similar to this one, with keywords mined from NFR catalogues found in their previous work~\cite{chung99}. 
They managed a recall of 80\% with precision of 57\% for the Security NFR, but could not find a reliable source of keywords for other NFRs. 
Instead, they developed a supervised classifier by using human experts to identify an NFR training set. 
Our work differed because we had a more comprehensive set of terms based on the taxonomy we chose.
We also wanted a common taxonomy that allows us to make cross-project comparison; this was not one of their objectives.
The objective of Cleland-Huang's study was to identify new NFRs for system development, yet our objective was to recover those latent NFRs from commit-log messages of the project. 
Another difference was that our data was far less structured than the requirements documents used in their study.
%There are several reasons we did not follow this route. 
%One, we believe we have a more comprehensive set of terms due to the taxonomy we chose. 
%Secondly, we wanted to compare across projects. 
%Their technique was not compared across different projects and the applicability of the training set to different corpora is unclear. 
%A common taxonomy allows us to make cross-project comparison. 
%Although subject to the assumption that all projects conceive of these terms in the same way.
%Thirdly, while the objective of Cleland-Huang's study was to identify new NFRs (for system development) our study assumes these NFRs are latent in the commit-log messages of the project.

@@

To evaluate our approach, we sought candidate systems that were mature projects and had openly accessible source control repositories. 
We selected systems from the same application domain, so the functional requirements would be broadly similar. 
We selected MySQL 3.23 and MaxDB 7.500 as they were open-source, partially-commercial database systems. 
MaxDB started in the late 1970s as a research project, and was later acquired by SAP. 
As of version 7.500, released April 2007, the project has 940 thousand lines of C source code\footnote{generated using David A. Wheeler's \emph{SLOCCount}, dwheeler.com/sloccount.}. 
The MySQL project started in 1994 and MySQL 3.23 was released in early 2001. 
MySQL contains 320 thousand lines of C and C++ source code.  
Choosing an older version of these projects allowed us to focus on projects which have moved further into the maintenance phase of the software life-cycle.

@@

\noindent \textbf{Creating a validation corpus} --- For MySQL 3.23 and MaxDB 7.500, we manually annotated each extracted topic in each period with the same NFR labels as \textsf{exp2} (software qualities). 
We looked at each period's topics, and assessed what the data --- consisting of the frequency-weighted word lists and messages --- suggested was the topic for that period. 
We were able to pinpoint the appropriate label using auxiliary information as well, such as the actual revisions and files that were related to the topic being annotated.
For example, for the MaxDB topic consisting of a message ``exit() only used in non NPTL LINUX Versions'', we tagged that topic \emph{portability}. 
%\todo[inline]{this confused people. Is it truly unsupervised? Yes, but it needs to be clearer.}
We compared against this data-set, but we also used the data-set for our supervised machine learning based topic classification. 
% A topic may have more than one matching keyword. % ok what?
%\todo[inline]{inter-rater reliability }
% \todo[inline]{There should be a section here which is about manual annotation. It is really important and it is required by both analyses. Plus we can tell them how.}

@@

% word list similarity
Using our three word lists (\textsf{exp1}, \textsf{exp2}, \textsf{exp3}), we labeled our topics where there was a match between a word in the list and the same word in the topic.
A \emph{named topic} is a topic with a matching label. 
All experiments were run on MaxDB 7.500 and MySQL 3.23 data. LDA
extracted 20 topics per period for each.
% Is this good enough
This labelling is unsupervised because the corpus is not derived from 
the project being labelled and we did not label the project's topics
ourselves for a training set. The theory behind this technique is that
because most software often addresses similar issues, we can use the
domain knowledge of software to label relevant topics.
\todo[inline]{Neil does this explain the unsupervised aspect well enough?}

Table \ref{tbl:wordlist} shows how many topics were labelled for MaxDB
and MySQL.

@@

\noindent \textbf{Analysis of the unsupervised labelling} -- Based on the labels, and our manual topic labelling, 
we compared the results of the unsupervised word matching approach. 
For each quality we assessed whether unsupervised labels matched the manual annotations.
Figure \ref{fig:maxdb-unsup-results} shows our results for MaxDB and MySQL. 
\todo[inline]{NEIL: this section should be updated to explain F-measure}
Our performance is measured using the Receiver Operating
Characteristic area-under-curve value~\cite{Fawcett2006861},
abbreviated \emph{ROC}, and the F-measure. 
ROC values provide a score, similar to school letter-grades (A is 0.9, C is 0.6), reflecting how well a particular learner performed for the given data. 
ROC maps to the more familiar concepts of precision/sensitivity and recall/specificity: it plots the true positive rate (sensitivity) versus the false positive rate (1 - specificity). 
A perfect learner has a ROC value of 1.0, reflecting perfect recall and precision. 
A ROC result of 0.5 would be equivalent to a random learner (that is, issuing as many false positives as true positives). 
The area under the ROC of a classifier is equivalent to the probability that the classifier will rank a randomly chosen positive instance higher than a randomly chosen negative instance.
F-measure is the harmonic mean of precision and recall.

%\todo[inline]{since ROC is new-sounding, I wonder if a more lengthy explanation would be merited. An obvious question is why not precision/recall? -- ROC is hot right now and it combines both}
% Rebuttal: ROC is not new and it is what the machine learning community, search based software engineering and now the MSR community are using +  it has natural meaningful quality mappings.
\begin{figure}
  \centering
 \includegraphics[width=0.45\textwidth]{figures/unsupervised-bar}
 \caption{Performance, ROC values (range: 0-1), of unsupervised topic labelling for
   each NFR and per word-list. Dashed line indicates the performance of a random classifier. This graph shows how well the
   unsupervised topic labelling matched our manual annotations.}

%\todo[inline]{this is too tiny in print}
  \label{fig:maxdb-unsup-results}
\end{figure}

\begin{figure}
  \centering
 \includegraphics[width=0.45\textwidth]{figures/unsupervised-bar-f1}
 \caption{Performance, F1 values (range: 0-1), of unsupervised topic labelling for
   each NFR and per word-list.}
  \label{fig:maxdb-unsup-results-f1}
\end{figure}

%\todo[inline]{where is exp1 report?}

%EXP1 could not be evaluated properly!
Because our ground truth annotations were only relevant to ISO-9126,
we estimate that \textsf{exp1} had poor
performance via the overlap between ISO-9126 and the Kayed ontology.
For \textsf{exp1} the F-measures for MaxDB were from $0$ to $0.18$ with an average
of $0.03$, and for MySQL were from $0$ to $0.16$ with an average of
$0.05$.
% 0.177215189873 / 6
% .02953586497883333333
% (0.0298507462687 + 0.0661157024793 + 0.0634920634921 + 0 + 0.115384615385) / 6
% .04580718793751666666

% EXP2 source is naming-paper/src/validate/exp2.maxdb.report.txt
% (change as needed). Second column (after the name) is F1.
For \textsf{exp2}, the average F-measure (macro-F1) for MaxDB was $0.24$ with a range $0.091$ to
$0.37$, and $0.16$ for MySQL with a range of $0$ to $0.41$.
MaxDB had an average precision and recall of $0.25$ and $0.22$
while MySQL had $0.41$ and $0.10$ respectively.

@@

Based on these results we find that \emph{reliability} and
\emph{usability} worked well for MaxDB in \textsf{exp2} and better in
\textsf{exp3}. 
\textsf{exp1} performed poorly.
MySQL had reasonable results within \textsf{exp2} for \emph{reliability} and \emph{efficiency}. 
MySQL's results for \emph{efficiency} did not improve in \textsf{exp3} but other qualities such as \emph{functionality} did improve. 
If a \emph{C} grade performance has a ROC value of $0.6$ then most of these tests scored a grade of \emph{C} or less, but our classifier nonetheless performed substantially better than random.
